\LARGE The Bitcoin Lightning Network:\\ \Large Scalable Off-Chain Instant Payments

### 2016-01-15 paper.tex
Fix a typo
Cross-Chain
We've been talking about cross-chain in person for a while (and on
IRC/mailing-lists/reddit), might as well add it in.

%opening
\title{\LARGE The Bitcoin Lightning Network:\\
	\Large Scalable Off-Chain Instant Payments}
\author{
		Joseph Poon\\
		\small\href{mailto:joseph@lightning.network}
			{\nolinkurl{joseph@lightning.network}}
	\and 
		Thaddeus Dryja\\
		\small\href{mailto:rx@awsomnet.org}
			{\nolinkurl{rx@awsomnet.org}}
	}
\date{\today\\\small DRAFT Version 0.5.9}
\begin{document}

@@

>>>>

%opening
\title{\LARGE The Bitcoin Lightning Network:\\
	\Large Scalable Off-Chain Instant Payments}
\author{
		Joseph Poon\\
		\small\href{mailto:joseph@lightning.network}
			{\nolinkurl{joseph@lightning.network}}
	\and 
		Thaddeus Dryja\\
		\small\href{mailto:rx@awsomnet.org}
			{\nolinkurl{rx@awsomnet.org}}
	}
\date{\today\\\small DRAFT Version 0.5.9.2}
\begin{document}

@@

	\item Cross-Chain Payments. So long as there are similar hash-functions
		across chains, it's possible for transactions to be routed over
		multiple chains with different consensus rules. The sender does
		not have to trust or even know about the other chains -- even
		the destination chain. Simiarly, the receiver does not have to
		know anything about the sender's chain or any other chain. All
		the receiver cares about is a conditional payment upon
		knowledge of a secret on their chain. Payment can be routed by
		participants in both chains in the hop. E.g. Alice is on
		Bitcoin, Bob is on both Bitcoin and X-Coin and Carol is on
		a hypothetical X-Coin, Alice can pay Carol without
		understanding the X-Coin consensus rules.
